MHF SCP Experiment Visualisations

### 2024-09-04 minos/outcomes/MHF_SCP_visualisations.Rmd
Tracking the universal_credit module (not in use yet) and changed the MHF_SCP_vis script back to original colours and plots

```{r}
scen.colour.list <- c('baseline', '£10', '£20',
               '£25', '£30',
               '£35', '£40', '£45',
               '£50', '£60', '£70',
               '£80', '£90', '£100')

@@

scen.list.full <- c('baseline', '10UniversalCredit', '20UniversalCredit',
               '25UniversalCredit', '30UniversalCredit',
               '35UniversalCredit', '40UniversalCredit', '45UniversalCredit',
               '50UniversalCredit', '60UniversalCredit', '70UniversalCredit',
               '80UniversalCredit', '90UniversalCredit', '100UniversalCredit')

@@

@@

```{r "lone_parent_function", include=FALSE}
compare_lone_parent <- function(comparison_scen) {
  scen.list <- c('baseline', comparison_scen)
  UC.lone_parent <- do.call(rbind, generate_df_list('priority_lone_parent', scen.list))

@@

>>>>

```{r}
scen.colour.list <- c('baseline', '£10', '£20',
               '£25', '£30',
               '£35', '£40', '£45',
               '£50', '£60', '£70',
               '£80', '£90', '£100') #, '£110', '£120', '£130')

@@

scen.list.full <- c('baseline', '10UniversalCredit', '20UniversalCredit',
               '25UniversalCredit', '30UniversalCredit',
               '35UniversalCredit', '40UniversalCredit', '45UniversalCredit',
               '50UniversalCredit', '60UniversalCredit', '70UniversalCredit',
               '80UniversalCredit', '90UniversalCredit', '100UniversalCredit')#,
               #'110UniversalCredit', '120UniversalCredit', '130UniversalCredit')

@@

# scen.list.10_130 <- c('baseline', '10UniversalCredit', '20UniversalCredit',
#                       '30UniversalCredit', '40UniversalCredit', '50UniversalCredit', 
#                       '60UniversalCredit', '70UniversalCredit', '80UniversalCredit', 
#                       '90UniversalCredit', '100UniversalCredit',
#                       '110UniversalCredit', '120UniversalCredit', '130UniversalCredit')

@@

```{r "lone_parent_function", include=FALSE}
compare_lone_parent <- function(comparison_scen) {
  scen.list <- c('baseline', comparison_scen)
  UC.lone_parent <- do.call(rbind, generate_df_list('priority_lone_parent_UC', scen.list))

@@

## Cost Ratio: £10 - £130 (Defunkt)

```{r}
#SF_12_cost_ratio(summary_type = 'UC', scen_list = scen.list.10_130)
#SF_12_cost_ratio_cumul(summary_type = 'UC', scen_list = scen.list.10_130)
```
